Analyzing Trends on the Characteristics of Notable People on Wikipedia

### 2024-12-14 paper/paper.qmd
rewording abstract of paper

---
title: "Analyzing Trends on the Characteristics of Notable People on Wikipedia"
subtitle: "Time Period and Occupation Strongly Associated with Individual Prominence"
author: 
  - Parth Samant
thanks: "Code and data are available at: [https://github.com/samantparth/Wikipedia-Historical-Prominence-Trends](https://github.com/samantparth/Wikipedia-Historical-Prominence-Trends)."
date: today
date-format: long
abstract: "Wikipedia is an online encyclopedia that contains information on millions of diverse subjects, arguably serving as a repository for human knowledge. In this paper, I analyzed a dataset of notable people on Wikipedia from 3500 BCE to 2018 AD to identify whether certain characteristics (such as age and gender) were correlated with prominence. The analysis found that occupation and time period were most strongly associated with prominence, with subregion and gender being less significant. This highlights how prominence between already notable people selects for different characteristics."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

>>>>

---
title: "Analyzing Trends on the Characteristics of Notable People on Wikipedia"
subtitle: "Time Period and Occupation Strongly Associated with Individual Prominence"
author: 
  - Parth Samant
thanks: "Code and data are available at: [https://github.com/samantparth/Wikipedia-Historical-Prominence-Trends](https://github.com/samantparth/Wikipedia-Historical-Prominence-Trends)."
date: today
date-format: long
abstract: "Wikipedia is an online encyclopedia that contains information on millions of diverse subjects, arguably serving as a repository for human knowledge. In this paper, I analyzed a dataset of notable people on Wikipedia from 3500 BCE to 2018 AD to identify whether certain characteristics (such as age and gender) were correlated with prominence. The analysis found that occupation and time period were most strongly associated with prominence, with factors affecting prominence among already notable individuals differing from those that initially lead to notability. The findings highlight how biases against groups may be amplified or minimized when strictly analysing subgroups like notable individuals."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---
